---
title: 'Fisheries Managment: Japan and Norway'
subtitle: "<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>"
author: "Keita Abe"
date: "2019/6/7"
output: 
  xaringan::moon_reader:
      css: [default, metropolis, metropolis-fonts] 
      lib_dir: libs
      nature:
        highlightStyle: github
        highlightLines: true
        countIncrementalSlides: false
---


```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
library(knitr)
opts_chunk$set(
  fig.align="center",  
  fig.height=4, #fig.width=6,
  # out.width="748px", #out.length="520.75px",
  dpi=300, #fig.path='Figs/',
  cache=T#, echo=F, warning=F, message=F
  )
library(tidyverse)
library(estatapi)
library(gghighlight)
#library(hrbrthemes)
```

# Table of contents

1. [Introduction](#intro)

2. [The Fisheries](#fisheries)

3. [Key Categolization](#category)

4. [Brief Hisotry](#history)

5. [Management](#management)

6. [Case Studies](#cases)

7. [Comparison of framework](#comparison)

8. [ITQs for Japanese Fisheries](#itq)


---
class: inverse, center, middle
name: prologue

# Introduction

<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>


---

# Fisheries Catch 

catch and value?

fishers and fisheries has been declining.
It is mainly because technological progress.


```{r estat, echo = FALSE}

appID <- "11217753824fd6ecf1d5cc2880b613e3ee724fdb"
## estat_getStatsList(appId = appID, searchWord = "海面漁業生産統計調査")

# data: 1979-2002
dat.annual1 = estat_getStatsData(
  appId = appID, 
  statsDataId = "0003229517"
)

# data from 2003-2012
dat.annual2= estat_getStatsData(
  appId = appID, 
  statsDataId = "0003229518"
)

# combine annual data.
dat.annual = bind_rows(dat.annual1,dat.annual2)

# data by species 0003238631
dat.species= estat_getStatsData(
  appId = appID, 
  statsDataId = "0003238631"
)


```


---
class: inverse, center, middle
name: fisheries

# The Fisheries

<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>

---

# Nature conditions 

```{r natural, echo = FALSE}

 if(FALSE){
   # OECD dummy and location of the capital data (compiled by hand)
   dat.oecd = read_csv("./data/oecd.csv") %>%
     mutate(capital_lat_NS = str_extract(Capital_lat,".$"),
                  capital_lon_EW = str_extract(capital_lon,".$"),
                  capital_lat = as.numeric(str_replace(Capital_lat,capital_lat_NS,"")),
                  capital_lon = as.numeric(str_replace(capital_lon,capital_lon_EW,""))) %>%
     mutate(OECD = ifelse(is.na(OECD),0,OECD)) %>%
     dplyr::select(Country,OECD,capital,capital_lat,capital_lat_NS,
                   capital_lon,capital_lon_EW)
   
   write_csv(dat.oecd, "./data/oecd2_capital_location.csv")
 }

dat.oecd = read_csv("./data/oecd2_capital_location.csv")

# Data is obtained from FishStatJ
dat.fao_catch = read_csv("./data/FishStat_world_catch_2010_2017.csv") %>%
           tidyr::gather(key = "year",value = "catch",-c(1:4)) %>%
           mutate(catch = ifelse(catch == "...",NA,
                                 ifelse(catch == "-",0,catch))) %>%
           mutate(catch = str_replace_all(catch," ",""),
                  catch = str_replace_all(catch,"F","")) %>%
           filter(`Unit (Unit)` != "Number") %>% # most of species with number is marine mammal (seal, whale, etc) 
           mutate_at(vars(year,catch),list(~ as.numeric(.)))
           # calculate the diversity measure (Shannon)

# make dataframe for lat x diversity by country (2010-2017 average)
dat.fao1 = dat.fao_catch %>%
           group_by(`Country (Country)`,`Species (ASFIS species)`) %>%
             summarise(catch = mean(catch,na.rm = TRUE)) %>%
           ungroup() %>%
           group_by(`Country (Country)`) %>%
             mutate(share = catch/sum(catch,na.rm = TRUE)) %>%
           ungroup() %>%
           mutate(log_share = ifelse(share == 0,0,log(share))) %>%
           filter(!is.nan(catch)) %>%
           mutate(share_log_share = share*log_share) %>%
           group_by(`Country (Country)`) %>%
             summarise(shannon = -1*sum(share_log_share,na.rm = TRUE)) %>%
           ungroup() %>%
           # merge OECD and capital location data
           left_join(dat.oecd,by = c("Country (Country)" = "Country")) %>%
           # only OECD countries
           filter(OECD == 1) %>%
           # remove shannon = 0 
           filter(shannon != 0)

           

ggplot(dat.fao1,aes(x = shannon,y = capital_lat)) + 
  geom_point() +
  # geom_smooth(method = "lm", se = FALSE) + 
  geom_text(aes(label=`Country (Country)`),hjust=-0.1, vjust=0, size = 3) + 
  gghighlight(label_key = `Country (Country)`, 
                  `Country (Country)` == "Norway" | `Country (Country)` == "Japan") +
theme_bw() + 
  labs(x = "Diversity index of catch, 2010-2017 Mean",
       y = "Latitude of capital city")
  

```


---

# Social conditions


```{r socialcondition,echo = FALSE}
dat.fao_catch_rank = dat.fao_catch %>%
                     group_by(`Country (Country)`,year) %>%
                       summarise(catch = sum(catch,na.rm = TRUE)) %>%
                     ungroup() %>%
                     filter(year == 2013) %>%
                     mutate(catch_rank = min_rank(desc(catch)),
                            rank40_d = ifelse(catch_rank <= 40,1,0))

dat.oecd2 = read_csv("./data/oecd.csv") %>%
           left_join(dat.fao_catch_rank,by = c("Country" = "Country (Country)"))

dat.fao2 = read_csv("./data/FAOSTAT_food_balanc_sheet.csv") %>%
           dplyr::select(-`Item Code`) %>%
           tidyr::spread(key = "Item",value = "Value") %>%
           left_join(dat.oecd %>% dplyr::select(Country,OECD, rank40_d), by = "Country") %>%
           # top 40 catching country + OECD
           filter(OECD == 1 | rank40_d == 1) %>%
           # for now, pick 2013. Can be changed among 2009-2013.
           filter(Year == 2013) %>%
           mutate(fish_rate = `Fish, Seafood`/`Animal Products`*100)

```


---

# How to characterize Japanese fisheries?



---
class: inverse, center, middle
name: category

# Key categolization




---

# Main categolization of Japanese fisheries


---

# Coastal Fisheries


---

# Offshore Fisheries


---

# Distant Water Fisheries (High Seas)


---
class: inverse, center, middle
name: history

# Brief History

<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>

---

---
class: inverse, center, middle
name: management

# Japanese Fisheries Management

<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>

---

# Objectives

---

# Scheme

---

# Fishing rights

---

# Fisheries cooperatives


--- 

# Resource management?


--- 

# Japasense TAC


---

# Policy reform in 2018


---
class: inverse, center, middle
name: cases

# Case Studies

<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>

---

# Coastal Fishery



---

# Glass Shrimp Fishery



---

# Offshore fishery



---

# Purse Seine fishery



---
class: inverse, center, middle
name: comparison

# Comparison of frameworks

<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>

---

# Summary of Japanese Fisheries

characteristics: natural/social conditions and hisotrical back ground.
co-management

---

# Difference?

Diff in schemes. 1genron - 2genron



---

# Outcome?



---
class: inverse, center, middle
name: itq

# ITQs for Japanese Fisheries

<html><div style='float:left'></div><hr color='#00BFFF' size=1px width=796px></html>

---


